The limits of self commitment and private paternalism \thanks{}

### 2020-06-16 main.tex
author edit

\title{Private paternalism and the limits of self commitment  \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement. We want to thank also Ricardo Olivares for excellent research assistance and Erik Molina help with formatting. Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin and seminar participants at ITAM provided very valuable feedback.}}
\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Sadka: ITAM, jsadka@itam.mx;  
Seira: ITAM, enrique.seira@itam.mx; Meza: University of California at Berkeley, isaac.meza@berkeley.edu} }
\date{This draft:  \today \\[2 cm]}

>>>>

\title{Private paternalism and the limits of self commitment  \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement. We want to thank also Ricardo Olivares for excellent research assistance and Erik Molina help with formatting. Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin and seminar participants at ITAM provided very valuable feedback.}}
\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
Seira: ITAM, enrique.seira@itam.mx} }
\date{This draft:  \today \\[2 cm]}
